\documentclass[11pt]{article}
\usepackage
[top = 1cm, 
bottom = 1cm,]
{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
% \usepackage{titlesec}

\title{Meeting Summary of May 5, 2025}
\date{}  % You can manually write the date in the document body
\author{}

\begin{document}

\maketitle

\noindent
\textbf{Date:} May 5, 2025 \\
\textbf{Time:} 2:30--3:15 PM \\
\textbf{Attendees:} Prof. Jan, Prof. Jabed, Prof. Zhang, Feng Gu \\
\textbf{Topic:} Establishing a general framework and drafting a proposal for Feng's thesis.

\vspace{1em}

\section*{Summary of Discussion}
\begin{itemize}[leftmargin=1.5em]
    \item The framework for the thesis program was discussed, focusing on using breakpoint analysis in (quantile)regression to extend the research of two dissertations.
    \item A general working schedule for the summer was discussed. Prof. Jabed will travel to Bangladesh for a period, while Prof. Jan is willing to hold online meetings and share datasets with Feng.
\end{itemize}

\section*{Decisions Made}
\begin{itemize}[leftmargin=1.5em]
    \item Feng will review the two dissertations suggested by Prof. Jan and attempt to understand and replicate the analysis.
    \item Feng will study and practice breakpoint analysis in regression, review the earlier work of Prof. Jabed and Prof. Jan published in 2020\footnote{\href{https://onlinelibrary.wiley.com/doi/epdf/10.1002/ece3.6955}{Click here for the paper}}, and examine an ongoing draft.
    \item Prof. Jan or Prof. Jabed will share the datasets used in the paper with Feng.
\end{itemize}

\section*{Action Items}
\begin{itemize}[leftmargin=1.5em]
    \item \textbf{Feng:} Summarize 2 dissertations by May 13.
    \item \textbf{Prof. Jan:} Share datasets.
\end{itemize}

\section*{Follow-Up}
Temporary meeting time: waiting to be confirmed.

\section{Attached Documents}
Some piecewise quantile regression figures from another finished paper were shared with Feng for reference.

\href{URL}{Click here to jump to the GitHub repository to check the figures.}

\end{document}