\documentclass[11pt]{article}
\usepackage
[top = 1cm, 
bottom = 1cm,]
{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
% \usepackage{titlesec}

\title{Meeting Summary of Mar 21, 2025}
\date{}  % You can manually write the date in the document body
\author{}

\begin{document}

\maketitle

\noindent
\textbf{Date:} Mar 21th, 2025 \\
\textbf{Time:} 10:00--10:20 AM \\
\textbf{Attendees:} Prof. Jan, Prof. Jabed, Prof. Zhang, Feng Gu \\
\textbf{Topic:} Establishing a general framework and drafting a proposal for Feng's thesis.
\textbf{GitHub repository:} \href{https://github.com/Gufeng-2002/Thesis_Meeting_Notes/tree/main/Mar_21th_25_meeting_notes}{Click here to jump to the GitHub repository.}

\vspace{1em}

\section*{Summary of Discussion}
\begin{itemize}[leftmargin=1.5em]
    \item Discussed and decided the supervisors and committee members for Feng's thesis.
    \item Confirmed the inaugural committee form for Feng's thesis program.
\end{itemize}


\section*{Action Items}
\begin{itemize}[leftmargin=1.5em]
    \item To finish the inaugural committee form and sign it by all members.
    \item To make a tentative topic for the committee form.
\end{itemize}

\section*{Follow-Up}
Temporary meeting time: waiting to be confirmed.

\section*{Supportive materials}
Two dissertations about Prof. Jan's research work were shared with Feng for reference.

\href{https://github.com/Gufeng-2002/Thesis_Meeting_Notes/tree/main/Mar_21th_25_meeting_notes/supportive_materials}{Click here to jump to the GitHub repository to check the figures.}

\end{document}